Spatiotemporal Visualization

### 2022-06-03 doc/spatiotemp-viz.Rmd
- chore: rename task cookfarm to `cookfarm_mlr3`

```{r, fig.align='center', eval=os&&!is_cran&&pkgdown, fig.width=8, fig.height=9}
library(mlr3)
library(mlr3spatiotempcv)
task_st = tsk("cookfarm")
resampling = rsmp("sptcv_cluto", folds = 5)
resampling$instantiate(task_st)

>>>>

```{r, fig.align='center', eval=os&&!is_cran&&pkgdown, fig.width=8, fig.height=9}
library(mlr3)
library(mlr3spatiotempcv)
task_st = tsk("cookfarm_mlr3")
resampling = rsmp("sptcv_cluto", folds = 5)
resampling$instantiate(task_st)
